Generation of TypeScript Declaration Files from JavaScript Code

### 2020-08-19 programming-2021/main.tex
Update example for github-url-to-object

declare function GithubUrlToObject(repoUrl: string|GithubUrlToObject.I__repoUrl, opts: undefined): object;
declare function GithubUrlToObject(repoUrl: string|GithubUrlToObject.I__repoUrl, opts: GithubUrlToObject.I__opts): null|object;
declare function GithubUrlToObject(repoUrl: GithubUrlToObject.I__repoUrl, opts: undefined): object;
declare namespace GithubUrlToObject {
  export interface I__repoUrl {
    'url': undefined | string;
  }

  export interface I__opts {
    'enterprise': undefined | boolean;
  }
}
    \end{lstlisting}
    \caption{github-url-to-object/index.d.ts - Generated with manually expanded code example}
  \end{subfigure}

@@

// Manually added:
gh('git+https://githuuub.com/monkey/business.git', {});
gh('git+https://githuuub.com/monkey/business.git', {enterprise: true});
gh({url: 'git://github.com/monkey/business.git'});

    \end{lstlisting}
    \caption{Code example for module \texttt{github-url-to-object}.}
    \end{subfigure}
  \caption{Manually expanded code example for \texttt{github-url-to-object} to match DefinitelyTyped declaration file. Literal interface in DefinitelyTyped gets replace by a declared interface. The \texttt{undefined} type is used instead of the optional type. Return types are not considered.}
  \label{fig:experiments-results-manually-completed-examples}
\end{figure}

We discovered only 8 modules with \texttt{unsolvable} differences. Most of them were
caused by the same error: 7 modules incorrectly declared an interface for the
\texttt{string} type. This interface contains standard properties and methods from the
JavaScript \texttt{String} object, such as \texttt{length} or \texttt{indexOf()}. The remaining module is \texttt{stream}
remaining modules are \texttt{duplexer2} and \texttt{duplexer3}. Both of them rely on native
NodeJS types within the declaration file, which \texttt{dts-generate} could not identify
properly.

>>>>

declare function GithubUrlToObject(repoUrl: string | GithubUrlToObject.I__repoUrl, opts?: GithubUrlToObject.I__opts): object | null;
declare namespace GithubUrlToObject {
  export interface I__repoUrl {
    'url'?: string;
  }

  export interface I__opts {
    'enterprise'?: boolean;
  }

}
    \end{lstlisting}
    \caption{github-url-to-object/index.d.ts - Generated with manually expanded code example}
  \end{subfigure}

@@

// Manually added:
gh('git+https://githuuub.com/monkey/business.git', {});
gh('git+https://githuuub.com/monkey/business.git', {enterprise: true});
gh({url: 'git://github.com/monkey/business.git'});
gh('this is not a proper url');
gh({url: 'this is not a proper url'});
    \end{lstlisting}
    \caption{Code example for module \texttt{github-url-to-object}.}
    \end{subfigure}
  \caption{Manually expanded code example for \texttt{github-url-to-object} to match DefinitelyTyped declaration file. Literal interface in DefinitelyTyped gets replace by a declared interface. The \texttt{undefined} type is used instead of the optional type. Return types are not considered.}
  \label{fig:experiments-results-manually-completed-examples}
\end{figure}

We discovered only 8 modules with \texttt{unsolvable} differences. Most of them were
caused by the same error: 7 modules incorrectly declared an interface for the
\texttt{string} type. This interface contains standard properties and methods from the
JavaScript \texttt{String} object, such as \texttt{length} or \texttt{indexOf()}.
